---
title: "R Notebook"
output: html_notebook
author: "Yasar Kakdas"
---

```{r warning=FALSE}
library(tidyverse)
library(googleway)
library(tmaptools)
```


```{r warning=FALSE}
source("ApiSecretKey.R")
source("create_query.R")
source("create_info_text.R")
source("magnitude_color.R")
source("statistics.R")
source("plotting.R")
```


## TEST SCENARIOUS


### 1. Run with default parameters, it will bring the latest earthquakes(last 30 days) from all over the world


```{r}
suppressWarnings(plot_earthquakes())
```



### 2. Run with specific address, it will bring the latest earthquakes(last 30 days) for 200km perimeter of the given address


```{r}
suppressWarnings(plot_earthquakes(address = "Japan"))
```




### 3. Run with specific address and date. (The earthquake that happened in February 2023 in Turkey is a good example)

```{r}
suppressWarnings(
  plot_earthquakes(
    address = "Kahramanmaras",
    starttime = "Feb 4 2023",
    endtime = "Feb 8 2023"
  )
)
```


### 4. Add max radius constraint for the last query

```{r}
suppressWarnings(
  plot_earthquakes(
    address = "Kahramanmaras",
    starttime = "Feb 4 2023",
    endtime = "Feb 8 2023",
    maxradiuskm = 75
  )
)
```


### 5. Add bounding box visualization for the last query

```{r}
suppressWarnings(
  plot_earthquakes(
    address = "Kahramanmaras",
    starttime = "Feb 4 2023",
    endtime = "Feb 8 2023",
    maxradiuskm = 75,
    show_bounding_box = T
  )
)
```



### 6. Show info window on hovering the circle

```{r}
suppressWarnings(
  plot_earthquakes(
    address = "Kahramanmaras",
    starttime = "Feb 4 2023",
    endtime = "Feb 8 2023",
    maxradiuskm = 75,
    show_bounding_box = T,
    show_info_window_on_hover = T
  )
)
```


### 7. Show info window on clicking the circle

```{r}
suppressWarnings(
  plot_earthquakes(
    address = "Kahramanmaras",
    starttime = "Feb 4 2023",
    endtime = "Feb 8 2023",
    maxradiuskm = 75,
    show_bounding_box = T,
    show_info_window_on_click = T
  )
)
```



### 8. Add min magnitude constraint for the last query

```{r}
suppressWarnings(
  plot_earthquakes(
    address = "Kahramanmaras",
    starttime = "Feb 4 2023",
    endtime = "Feb 8 2023",
    maxradiuskm = 75,
    show_bounding_box = T,
    show_info_window_on_click = T,
    minmagnitude = 5.5
  )
)
```


